Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-09-18 draft/draft0.tex
update draft

Dark energy has become the most important scientific issue since the discovery of cosmic acceleration \citep{Riess1998,Perl1999}.
Many theoretical and observational effect has been made \citep{Weinberg,Li2011,DHW2013}, but its properties still remain far from accurately known and its nature still remains mystery. 
%The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.

To measure the properties dark energy we need accurate probe of the cosmic expansion history. 
In large scale structure surveys the two representative geometrical observables are the angular diameter distance $D_A$ and the Hubble factor, $H$. 
If these can be precisely measured as functions of redshift, then tight constraints can be placed on the parameters of the cosmological model,
e.g., the matter density $\Omega_m$ and the equation of state (EoS) of dark energy, $w$.

Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space leaves residual geometric distortions. 
These distortion include volume effect which is the alteration of the comoving volume size of structures,
and the Alcock-Paczynski (AP) effect, induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
%There have been a series of works studying the application of the AP test to the LSS
A series of statistically method has been proposed to measure the AP test in the LSS
\citep{Ballinger1996,Matsubara1996,Marinoni2010,Ryden1995,LavausWandelt1995}
and have been applied to a series of LSS surveys \citep{Outram2004,Blake2011,ChuangWang2012,
Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,
Alam2016, Beutler2016, Sanchez2016,Qingqing2016}. 
The probe of volume effect is usually probed through number counting of 
galaxy clusters \citep{PS1974,VL1996}, topology \citep{topology};
it is also part of the physical effects measured in the measurements of the BAO scale \citep{some reference},
or the probe of the shape of 2pCF and power spectrum \citep{some reference}.

@@

@@

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138

@@

%\bibitem[Jeong et al.(2014)]{Jeong2014}
%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

@@

%\bibitem[Sutter et al.(2014)]{Sutter2014}
%Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983

\bibitem[Salvador et al. (2014)]{Salvador2014}
Salvador, S.A., S\^{a}nchez, A.G., Padilla, N.D., \& Baugh, C.M. 2014, MNRAS, 443, 2612

\bibitem[Salvador et al. (2016)]{Salvador2016}
Salvador, S.A., S\^{a}nchez, A.G., \& Grieb, J.N., et al. 2016, submitted to MNRAS

\bibitem[Sanchez et al.(2016)]{Sanchez2016}
Sanchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
arXiv:1607.03147

@@

>>>>

The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
or the breakdown of Einstein's gravity theory on cosmological scales.
The theoretical explanation and observational probe of cosmic acceleration has attracted 
tremendous effort in the last two decades and are still far from well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
%, but its properties still remain far from accurately known and its nature still remains mystery. 
%The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.

In an effort to probe the cosmic expansion history the large scale structure (LSS) surveys enable measurements of two geometrical quantities, 
the angular diameter distance $D_A$ and the Hubble factor, $H$. 
If they were precisely measured as a function of redshift, 
tight constraints can be placed on cosmological parameters, 
e.g. the matter density $\Omega_m$ and the equation of state (EoS) of dark energy $w$.

As one geometrical effect of cosmological parameters on LSS,  
when an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
geometric distortions are produced in the constructed galaxy distribution. 
These distortion include the ``volume effect'' which is the mis-scaling of the size of structures,
and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
%There have been a series of works studying the application of the AP test to the LSS

Various statistically methods has been proposed to measure these effects.
The AP effect has been proposed to measure through the clustering of galaxies \citep{Ballinger1996,Matsubara1996} which has been applied to a series of LSS surveys
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
the alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed able to probe the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

%\bibiem[Kazin et al (2012)]{KSB2012}
%Kazin, E.A., S\'{a}nchez, A.G., Blanton, M.R. 2012, MNRAS, 419, 3223

@@

\bibitem[Blake \& Glazebrook (2003)]{BG03};
 Blake, C., \& Glazebrook, K. 2003, ApJ, 594, 665

@@

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138
\bibitem[Eisenstein et al. (1998)]{EHT1998}
Eisenstein, D.J., Hu, W., \& Tegmark, M. 1998, ApJ, 504, L57

@@

\bibitem[Jeong et al.(2014)]{Jeong2014}
Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

@@

\bibitem[Sutter et al.(2014)]{Sutter2014}
Sutter, P.M., Pisani, A., Wandelt, B.D., \& Weinberg, D.H. 2014, MNRAS, 443, 2983

\bibitem[Salvador et al. (2014)]{Salvador2014}
Salvador, S.A., S\'{a}nchez, A.G., Padilla, N.D., \& Baugh, C.M. 2014, MNRAS, 443, 2612

\bibitem[Salvador et al. (2016)]{Salvador2016}
Salvador, S.A., S\'{a}nchez, A.G., \& Grieb, J.N., et al. 2016, submitted to MNRAS

\bibitem[S\'{a}chez et al. (2006)]{Sanchez2006}
S\'{a}chez, A.G., Baugh, C.M., \& Percival, W.J. et al. 2006, MNRAS, 366, 187

\bibitem[S\'{a}nchez et al. (2009)]{Sanchez2009}
S\'{a}nchez, A. G., Crocce, M., Cabr\'{e}, A., Baugh, C.M., \& Gaztaaga, E. 2009, MNRAS, 400, 1643

\bibitem[Sanchez et al.(2016)]{Sanchez2016}
S\'{a}nchez, A. G., Scoccimarro, R., \& Crocce, M., et al.
arXiv:1607.03147

@@

\bibitem[Seo \& Eisenstein (2003)]{SE03}
Seo, H.-J., \& Eisenstein, D.J. 2003, ApJ, 598, 720
